\Large \bf One-Step, Three-Factor Authentication With Custom-Fit, In-Ear EEG

### 2017-02-14 paper.tex
typo

7 male participants (P1-P7), 5 students and 2 non-students, completed our study protocol that was approved by our local Institutional Review Board. Three study visits took place per participant, in the first the 3D molds of participants' ears to use in creating the earpieces were obtained, the second to do a fit and electrical impedance check once earpieces were manufactured, and a third to collect data using the earpieces while participants performed a set of mental tasks to be used in authentication analysis. Informed consent was obtained prior to study procedures. The third study visit consisted of participants completing a short demographics questionnaire, a set up period with the openBCI system and earpieces including a second impedance check, the performance of 9 mental tasks presented on a laptop, and finally a post-experiment questionnaire. Approximately two weeks after the third study visit, a subset of participants reported via e-mail whether or not they remembered the passthoughts they chose and performed.

>>>>

7 male participants (P1-P7), 5 students and 2 non-students, completed our study protocol that was approved by our local Institutional Review Board. Three study visits took place per participant, in the first the 3D molds of participants' ears to use in creating the earpieces were obtained, the second to do a fit and electrical impedance check once earpieces were manufactured, and a third to collect data using the earpieces while participants performed a set of mental tasks to be used in authentication analysis. Informed consent was obtained prior to study procedures. The third study visit consisted of participants completing a short demographics questionnaire, a set up period with the OpenBCI system and earpieces including a second impedance check, the performance of 9 mental tasks presented on a laptop, and finally a post-experiment questionnaire. Approximately two weeks after the third study visit, a subset of participants reported via e-mail whether or not they remembered the passthoughts they chose and performed.
